Predicting sales of newly published books

### 2015-08-18 paper.tex
contestando algunos comentarios
contestando algunos comentarios más
contestando algunos comentarios más.
arreglando (rehaciendo) la sección del estado del arte
SoA: comentando sobre la ausencia de trabajos sobre predicción de ventas de libros.
añado los resultados de MP5, LR y KNN. Aún faltan los de SVM y MLP
Completo la tabla results13 . Aún faltan los de SVM y MLP en la tabla results7
Ya están los resultados de SVM para tabla results7 . Aún faltan los de MLP en la tabla results7
rehaciendo el estado del arte

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
The company's expert sales managers analized historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.

@@

In the literature several proposals to perform the prediction of sales
in different fields can be found. % frase que no dice nada. ¿Por qué no empiezas enmarcando el estado del
                                % arte? Methods to predict book sales have been generally based on ... - JJ
                                % [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
                                %  por eso quiero enfocarlo desde el punto de vista de la predicción 
                                %  de ventas en general, que sí hay bastante en muchos campos.
On the one hand, several qualitative methods are based on an expert
experience, while time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
are based on using historical data to make predictions
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
                                % dicho cuál es el problema. Tienes
                                % que decir claramente qué tienes y
                                % qué quieres. - JJ

Although using time series prediction methods is perhaps the most used
technique to tackle the sales forecasting task, the efficiency of these 
techniques depends largely on the field of application and the problem data. 
Specifically, techniques that require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

Thus, in the last years, different analysis and forecasting methods 
have been proposed for sales forecasting in several industry fields. %similar to the publishing industry.

  %[Pedro] el caso de la industria de la moda es muy similar al de la 
  % publicación de nuevos libros, ya que no hay datos históricos 
  % de un nuevo producto, y hay que echar mano de productos similares
  % o simplemente de los datos que describen el nuevo producto.
In the fashion industry, very similar to the publishing industry, 
predicting sales is a very complex problem, subject
to certain specific requirements \cite{SThomassey2014}.
This task has been faced using various methods in recent decades
  %[Pedro] me falta describir las aproximaciones
\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre
  % New tea product
  % New cosmetic product
  % New soft drink product

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre 
  % sales forecasting in printed circuit board industry

Finally, in many cases the predictions are influenced by external 
variables that must be taken into account, such as seasonality, 
promotions or fashions \cite{Lapide1999,ChingChin2010,ChernWSF15}.
In this sense, some authors propose reducing variations in the data 
caused by such variables to improve the accuracy of predictions
 \cite{Sheikh2003,Schrieber2005}.

%On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
%However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.

Taking into account the kind of problem we address in this paper, the 
classical forecasting methods are not useful. 
Thus, we must analyze raw data using other tools, prior to apply 
forecasting techniques.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are proposed.

@@

Finally, in the literature different error measures can be found to report the results obtained using the prediction methods. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).

In any case, we recommend using widely accepted standard equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} in order to compare obtained results with those presented in other research papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.

@@

Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] ¿a qué gráficas te refieres? ¿a las tablas de las variables?
% NO, a fig:som43, creo, porque ha desaparecido. - JJ
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som13vars.eps,width=11cm} \\
  \epsfig{file=som13umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Análisis de los datos iniciales, usando 13 variables
    descriptivas por libro, utilizando el SOM.}}
%describir de forma más precisa: visualización usando UMatrix de... -
%JJ
% ¡y usar nombres en inglés para las variables! - JJ
\label{fig:som13}
\end{center}
\end{figure}

@@

  %[pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados.
Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	& MAE 			& RMSE 			& RAE 			& RRSE 			\\
\hline
  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

 % [Pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
Obtained results using the different forecasting methods on the dataset with 7 variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	& MAE 			& RMSE 			& RAE 			& RRSE 			\\
\hline
  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

>>>>

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
The company's expert sales managers analized historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.

%In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.

@@

% [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
%  por eso quiero comenzar hablando de la aplicación de métodos
%  de predicción en la industria en general, que sí hay bastante bibliografía.

% In the literature several proposals to perform the prediction of sales in different fields can be found. 
In the last years, different analysis and forecasting methods, such as
regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001} 
have been applyed in different industry sectors, i.e. electricity consumption, traffic flow or sales forecasting.

Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems, 
the efficiency of these techniques depends largely on the field of application 
and the problem data as they require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

This is the new book sales forecasting case, for which no historical data 
to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008} is available
and only some descriptive variables relative to the new unpublished-book are available.

Methods used to predict book sales have been generally based on experts' 
experience who analyzed data about sales, and taking into account their knowledge 
in industry experience and their perception about trends, could make decisions
on the companies production (how many books should be printed when a new book is published).
This a complex problem as the predictions are influenced by external variables 
that must be taken into account, such as seasonality, promotions or fashions 
that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose \cite{Moon2010ICSSSM,Moon2010ICEC} analyzing 
relationships between on-line information and book sales.
Specifically, authors propose using the number of blog references as an indicator of book sales.
Different sales patterns are observed by analyzing data obtained.
In any case, in this research, historical data from published books is used, 
and the proposed methodology can not be usable in the problem of unpublished-books sales prediction.

%
% pasar a contar los casos de la predicción de ventas en la 
% industria de la moda (SThomassey2014) y de nuevos productos (ChingChin2010)
%
% Son problemas muy similares, ya que no hay datos históricos de los nuevos productos,
% al igual que no los hay sobre ventas, y en los que además influyen mucho las variables 
% externas (estacionalidad, modas, fama del author, etc).
% Hay que echar mano de productos similares o simplemente de los datos que describen el nuevo producto.
%

Some authors have faced the problem of forecasting sales of new products using 
different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
decision trees for sales forecasting in textile-appared fashion industry, 
a very similar issue to the new book publishing problem.
The same problem was previously faced by Xia et al \cite{Xia2012} using a 
forecasting method based on extreme learning machine with adaptive metrics of inputs.
Complexity of this problem is due to the lack of historical data, short lifetime 
of the large number of items, and due to the influence of variables such as promotions, 
fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.

%Finally, although different authors have proposed metrics to determine 
%the accuracy of estimates, most companies use metrics based on the analysis 
%of errors, i.e. MAE or RMSE \cite{ChingChin2010,Madsen2008}.

Taking into account the kind of problem we address in this paper, 
a new product sales prediction for which no historical data is available,
the classical forecasting methods based on time series are not adequate. 
Thus, in this paper the relevant variables in the prediction of sales are determined
using data visualization tools and then, standard data mining software 
to predict sales is used to deduce print roll.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are tested as an alternative.

@@

Finally, in the literature different error measures can be found to report the results obtained using the prediction methods. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} in order to compare obtained results with those presented in other research papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.

@@

Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som13vars.eps,width=11cm} \\
  \epsfig{file=som13umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Análisis de los datos iniciales, usando 13 variables
    descriptivas por libro, utilizando el SOM.}}
% describir de forma más precisa: visualización usando UMatrix de... - JJ
% ¡y usar nombres en inglés para las variables! - JJ
%[pedro] es el siguiente arreglo que le haré mañana al paper    ;)
\label{fig:som13}
\end{center}
\end{figure}

@@

  %[pedro] ya están todos los resultados de tabla:results13 para MP5, LR, KNN, SVM y MLP

  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE 		& RRSE 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	& 65.49 	& 133.73 	& 11.10 	& 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	& 100.813 & 257.63 	& 17.09 	& 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	& 52.30	  & 139.45	& 8.87    & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	& 198.16 	& 542.93 	& 33.59 	& 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	& 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN los de MLP

  Obtained results using the different forecasting methods on the dataset with 7 variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)     & MAE       & RMSE    & RAE     & RRSE      \\
\hline
  MP5     & 7.39 $\pm$ 1.75   & 117.78   & 260.05  & 18.51   & 17.00  \\
\hline
  LR      & 40.59 $\pm$ 12.94 & 120.29  & 252.91  & 18.91   & 16.54   \\
\hline
  SVM     & 1547.91 $\pm$ 365.55 & 109.30  & 251.16   & 17.18     & 16.42   \\
\hline
  KNN     & 0.02 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
\hline
  MLP     & 3265.71 $\pm$ 813.37   & 992.97 $\pm$ 0   & 1755.62 $\pm$ 0  & 156.07 $\pm$ 0   & 114.79 $\pm$ 0   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}
